Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
more forged results before I go home

\subsection{Subsurface Scattering and Deformation}
We first replicated \cite{Bickel:2010} to 
print materials with specified elasticity.
We then combined it with subsurface scattering
matching to print material that approximates
both the subsurface scattering property and the deformation behavior.
The result is shown in Figure~\ref{fig:deform}.
%We tried different combinations of generators in this experiment.
%We compared the performance of these different generator
%in terms of run-time and error.
\begin{enumerate}
\item Spline for top layer, fine-grained voxelization for mid layer
and a coarse grid for bottom layer.
\item Voxels for top layer, splines for middle layer and a coarse
bottom layer.
\item Find-grained voxels for top layer and coarse grid for bottom layer.
\end{enumerate}

@@

\subsection{New Examples for Mechanical Properties}
Ball bounce to certain height. We used a higher resolution
grid for the out layer and very low resolution
for the inner mesh.

A plot of bounce height after each iteration.
The height and desired height is plotted in Figure~\ref{fig:ball}
\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
	Redline is desired height.}
\label{fig:ball}
\end{figure}

A loaded die as shown in Figure~\ref{fig:die}. This example is interesting because
a local change will have some global effect.
We used very high resolution grid for the surface to match texture
of a die. The inner lay has only $3\times 3$ resolution.
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.

>>>>

\subsection{Subsurface Scattering and Deformation}
We first replicated \cite{Bickel:2010} to 
print materials with specified elasticity.
We then combined it with subsurface scattering
matching to print material that approximates
both the subsurface scattering property and the deformation behavior.
The result is shown in Figure~\ref{fig:deform}.
The combination is done by simply alternating tuners for the two
separate problems.
%We tried different combinations of generators in this experiment.
%We compared the performance of these different generator
%in terms of run-time and error.
%\begin{enumerate}
%\item Spline for top layer, fine-grained voxelization for mid layer
%and a coarse grid for bottom layer.
%\item Voxels for top layer, splines for middle layer and a coarse
%bottom layer.
%\item Find-grained voxels for top layer and coarse grid for bottom layer.
%\end{enumerate}

@@

\subsection{New Examples for Mechanical Properties}
%Ball bounce to certain height. We used a higher resolution
%grid for the out layer and very low resolution
%for the inner mesh.
%
%A plot of bounce height after each iteration.
%The height and desired height is plotted in Figure~\ref{fig:ball}
%\begin{figure}
%	\centering
% 	\includegraphics[width=0.3\textwidth]{figure/ballHeight.pdf}
%\caption{Simulated height per-iteration of a ball bouncing after free-falling at 1 meter height.
%	Redline is desired height.}
%\label{fig:ball}
%\end{figure}

A loaded die as shown in Figure~\ref{fig:die}. 
This example is a showcase for a global optimization algorithm
because a local change of material assignment will influence the global behavior.
We used very high resolution grid for the surface to match texture
of a die. The inner lay has only $3\times 3$ resolution.
\begin{figure}
	\centering
 	\includegraphics[width=0.25\textwidth]{figure/die.png}
\caption{A printed loaded die}
\label{fig:die}
\end{figure}
It has a certain probability to land on "1".
A table of probability distribution of landing on each side
is shown in Table~\ref{tab:dice}.
